ANTs in science

### 2015-05-20 evaluation/antsvfreesurfer2_extra.Rmd

*  "_Hey, can I have the FreeSurfer measurements for the entorhinal cortex?_"  <span style="color:blue;">Sure, why not?</span>

*  "_I was wondering if you would make available the CT in each ROI for each subject..._" <span style="color:blue;">Sure, why not?  Would you also like the surface areas and volumes?</span>

*  "_Can I have one or more of the templates that you used for your study?_"  <span style="color:blue;">Would you like the priors as well?</span>

*  "_Hey Nick, can we hire you to do an [EZ-MAP]-type study?_" <span style="color:blue;">What about something better?</span>

@@

__ANTs tools are multivariate__

<div align="center"><img height="450" src="./evaluation/figures/rfRmse0.5ANTsT1T2.png" frameborder="0"></img></div>

__Arno-thick-in-the-head (ATITH)__

<br><br>
<span style="color:blue;">_What if we made a crude estimate of the cortical thickness?_</span>
<br><br>

$thickness_{ROI} = \frac{volume_{ROI}}{area_{ROI}}$

<span style="color:blue;">Make sure you estimate the [surface area](http://www.insight-journal.org/browse/publication/852) correctly!</span>

@@

__Prediction from cortical thickness data:<br>gender and age__

<div align="center"><img height="350" src="./evaluation/figures/atith.png" frameborder="0"></img></div>

@@

@@

~~~~~~~~~~~~~~~~~~~~~~
$ DenoiseImage

@@

     --help
          Print the help menu.
~~~~~~~~~~~~~~~~~~~~~~

@@

~~~~~~~~~~~~~~~~~~~~~~~
${ANTSPATH}/antsCorticalThickness.sh \
  -a IXI/T1/IXI002-Guys-0828-T1.nii.gz \
  -e IXI/template/T_template0.nii.gz \
  -m IXI/template/T_template0ProbabilityMask.nii.gz \
  -f IXI/template/T_template0ExtractionMask.nii.gz \
  -p IXI/template/Priors/priors%d.nii.gz \
  -o IXI/ANTsResults/IXI002-Guys-0828-
~~~~~~~~~~~~~~~~~~~~~~~

@@

## Don't worry,

we'll run a 2-D example this afternoon.
<BR><BR>

@@

# Extensions

>>>>

*  "_Hey, can I have the FreeSurfer measurements for the entorhinal cortex?_"  Sure, why not?

*  "_I was wondering if you would make available the CT in each ROI for each subject..._" Sure, why not?  Would you also like the surface areas and volumes?

*  "_Can I have one or more of the templates that you used for your study?_" Would you like the priors as well?

@@

## ANTs tools are multivariate

![](./evaluation/figures/rfRmse05ANTsT1T2.png)

## Arno-thick-in-the-head (ATITH)

_What if we made a crude estimate of the cortical thickness?_

$$thickness_{ROI} = \frac{volume_{ROI}}{area_{ROI}}$$

## Make sure you estimate the [surface area](http://www.insight-journal.org/browse/publication/852) correctly!

@@

## Prediction from cortical thickness data

![](./evaluation/figures/atith.png)

## Brain constellation maps

@@

## Contribution from Jose

@@

```bash
$ DenoiseImage

@@

     --help
          Print the help menu.
```

@@

```bash
${ANTSPATH}/antsCorticalThickness.sh \
  -a IXI/T1/IXI002-Guys-0828-T1.nii.gz \
  -e IXI/template/T_template0.nii.gz \
  -m IXI/template/T_template0ProbabilityMask.nii.gz \
  -f IXI/template/T_template0ExtractionMask.nii.gz \
  -p IXI/template/Priors/priors%d.nii.gz \
  -o IXI/ANTsResults/IXI002-Guys-0828-
```

@@

## We'll discuss more this afternoon

@@

### 2015-05-20 installation/ants_installation.Rmd
ENH:  More material.

##

ANTs is a <span style="color:red;">_dynamic_</span> toolkit so,

@@

for the willing, we recommend compiling from source.

@@

##

@@

~~~~~~~~~~~~~~~~~~
$ cd ${WHICH_PATH}
$ git clone https://github.com/stnava/ANTs.git
$ cd ANTs
$ mkdir bin
$ cd bin
$ ccmake ..
$ make
$ echo "export ANTSPATH=/${WHICH_PATH}/ANTs/bin/bin/" >> ~/.profile
$ echo "export ITK_GLOBAL_DEFAULT_NUMBER_OF_THREADS=4" >> ~/.profile
$ source ~/.profile
~~~~~~~~~~~~~~~~~~

##

<span style="color:blue;">__Some cmake considerations:__</span>

@@

##

Try calling the <span style="color:blue;">```KellyKapowski```</span> short help menu.

~~~~~~~~~~~~~~~~~~
$ KellyKapowski -h

@@

OPTIONS:
     -d, --image-dimensionality 2/3
     -s, --segmentation-image imageFilename
                              [imageFilename,<grayMatterLabel=2>,<whiteMatterLabel=3>]
     -g, --gray-matter-probability-image imageFilename
     -w, --white-matter-probability-image imageFilename
     -c, --convergence [<numberOfIterations=50>,<convergenceThreshold=0.001>,<convergenceWindowSize=10>]
     -t, --thickness-prior-estimate thicknessPriorEstimate
     -a, --thickness-prior-image thicknessPriorFileName
     -r, --gradient-step stepSize
     -l, --smoothing-variance variance
     -m, --smoothing-velocity-field-parameter variance
                                              isotropicMeshSpacing
     -b, --use-bspline-smoothing 1/(0)
     -n, --number-of-integration-points numberOfPoints
     -p, --maximum-number-of-invert-displacement-field-iterations numberOfIterations
     -o, --output imageFileName
                  [imageFileName,warpedWhiteMatterImageFileName]
     -v, --verbose (0)/1
     -h
     --help
~~~~~~~~~~~~~~~~~~

##

or the <span style="color:blue;">```antsRegistration```</span> long help menu.

>>>>

## ANTs is a _dynamic_ toolkit

@@

so we generally recommend compiling from source.

Current modifications: ``antsAI`` and ``CreateTieldMosaic``.

@@

## First source for documentation

@@

```bash
$ cd ${WHICH_PATH}
$ git clone https://github.com/stnava/ANTs.git
$ cd ANTs
$ mkdir bin
$ cd bin
$ ccmake ..
$ make
$ echo "export ANTSPATH=/${WHICH_PATH}/ANTs/bin/bin/" >> ~/.profile
$ echo "export ITK_GLOBAL_DEFAULT_NUMBER_OF_THREADS=1" >> ~/.profile
$ source ~/.profile
```

## Some cmake considerations

@@

## Try calling the ```KellyKapowski``` short help menu.

```bash
$ KellyKapowski -h

@@

OPTIONS:
     -d, --image-dimensionality 2/3
     -s, --segmentation-image imageFilename
                              [imageFilename,<grayMatterLabel=2>,<whiteMatterLabel=3>]
     -g, --gray-matter-probability-image imageFilename
     -w, --white-matter-probability-image imageFilename
     -c, --convergence [<numberOfIterations=50>,<convergenceThreshold=0.001>,<convergenceWindowSize=10>]
     -t, --thickness-prior-estimate thicknessPriorEstimate
     -a, --thickness-prior-image thicknessPriorFileName
     -r, --gradient-step stepSize
     -l, --smoothing-variance variance
     -m, --smoothing-velocity-field-parameter variance
                                              isotropicMeshSpacing
     -b, --use-bspline-smoothing 1/(0)
     -n, --number-of-integration-points numberOfPoints
     -p, --maximum-number-of-invert-displacement-field-iterations numberOfIterations
     -o, --output imageFileName
                  [imageFileName,warpedWhiteMatterImageFileName]
     -v, --verbose (0)/1
     -h
     --help
```

## ```antsRegistration``` long help menu.

### 2015-05-20 installation/snap_installation.Rmd

~~~~~~~~~~~~~~~~~~~~~~~
$ tar -zxvf itksnap-3.2.0-rc2-20140919-Linux_x86_64.tar.gz
$ sudo cp itksnap-3.2.0-rc2-20140919-Linux_x86_64/ /usr/local/
$ itksnap
~~~~~~~~~~~~~~~~~~~~~~~

## Thanks Paul!

and [others](http://www.itksnap.org/pmwiki/pmwiki.php?n=Main.Credits)

>>>>

## Linux (command line)

```bash
$ tar -zxvf itksnap-3.2.0-rc2-20140919-Linux_x86_64.tar.gz
$ sudo cp itksnap-3.2.0-rc2-20140919-Linux_x86_64/ /usr/local/
$ itksnap
```

## Ready to go!
